API design for machine learning software: experiences from the scikit-learn project

### 2013-08-05 paper.tex
As it was, this sentence gave little information

\citet{pedregosa2011} briefly presented \sklearn and
benchmarked it against several competitors.
In this paper, we instead present an
in-depth analysis of design choices made when building the library,
detailing how we organized and operationalized
common machine learning concepts.
We first present in section~\ref{sec:core-api} the central application
programming interface (API) and then describe, in section~\ref{sec:advanced-api},
advanced API mechanisms built on the core interface.
Section~\ref{sec:implementation} briefly describes the implementation.
Section~\ref{sec:comparison} then
compares \sklearn to other major projects in terms of API\@.
Section~\ref{sec:future_work} outlines some of the work to be done before
a \sklearn 1.0 release.
We summarize and conclude in section~\ref{sec:conclusions}.

>>>>

\citet{pedregosa2011} briefly presented \sklearn and
benchmarked it against several competitors.
In this paper, we instead present an
in-depth analysis of design choices made when building the library,
detailing how we organized and operationalized
common machine learning concepts.
We first present in section~\ref{sec:core-api} the central application
programming interface (API) and then describe, in section~\ref{sec:advanced-api},
advanced API mechanisms built on the core interface.
Section~\ref{sec:implementation} briefly describes the implementation.
Section~\ref{sec:comparison} then
compares \sklearn to other major projects in terms of API\@.
Section~\ref{sec:future_work} outlines some of the objectives for
a \sklearn 1.0 release.
We conclude by summarizing the major points of this paper in
section~\ref{sec:conclusions}.
